SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-11-12 docs/questioning.tex
work on the conclusions

In this paper we first introduced an exploitation model
that can be a reference point which can be used by
researchers who wish to develop new countermeasures.

@@

\begin{itemize}
\item We believe that our research may facilitate researchers
or practitioners who would like to use one of the
aforementioned mechanisms and researchers who would like
to build new ones. Especially in the second case,
researchers can utilize our exploitation model as a
starting point to develop their approach.
\item We believe that forming a
standard way to test such mechanisms in terms
of accuracy and computational performance
would be one of the reasons of adopting them.
\end{itemize}

>>>>

In our research we tried to identify some of the reasons
why this is the case. Some of these reasons include
poor testing, high overhead, code unavailability,
deployment and security issues. However, our
systematization suggests that there are many
promising cases. For instance there are
many mechanisms that seem to have been extensively
tested in terms of accuracy ({\sc sqlc}eck, {\sc amnesia},
{\sc dsi}, libAnomaly), solve specific
problems in an efficient way (Blueprint and the system
by Stock et al.) or have a low computational overhead
({\sc dsi} and the system by Phung et al.).
There are also cases that researchers have made their
code available ({\sc beep} and {\sc sd}river) which
can be a push towards the development of better mechanisms.
Apart from making the source code of such mechanisms
available, we also believe that testing them in
a production setting could propel their adoption.

% First, we introduced an exploitation model
% to show how defense mechanisms can be seen
% from a common point of view. Our model can
% be a reference point for researchers who wish to develop
% new countermeasures. Then we categorized the various
% mechanisms and analyzed them based on specific criteria.
% We observed that the various mechanisms

@@

% \begin{itemize}
% \item We believe that our research may facilitate researchers
% or practitioners who would like to use one of the
% aforementioned mechanisms and researchers who would like
% to build new ones. Especially in the second case,
% researchers can utilize our exploitation model as a
% starting point to develop their approach.
% \item We believe that forming a
% standard way to test such mechanisms in terms
% of accuracy and computational performance
% would be one of the reasons of adopting them.
% \end{itemize}
